Generalised gravitational burst generation with Generative Adversarial Networks

### 2020-09-11 Paper_draft/main.tex
New edits and complete comments to section 4

% basic network structure
%
A neural network contains many single neurons connected in a layered structure
as shown in~\cref{fig:network}. The activation's of the first layer (or
input layer) act as the inputs to the second layer and so on until the output
layer. Multi-layered neural networks have intermediate layers between the input
and output stages dubbed the hidden layers.

% the cost or loss function
%
The output of a single neuron is gives a
prediction that can be compared to the real value through a loss (also known as a
cost) function. The network must work to minimise this function by updating the weights in the negative
direction of the loss gradient in a process referred to as gradient
descent \cite{ruder2016overview}. The training process for a single layered network is easy to compute as the weights relate directly to the gradient of the loss function the network is trying to minimise. For deeper architectures, the loss is a complicated function of all the weights in all the layers. The backpropagation \cite{Nielsen1992} algorithm acts over the many paths from node to output. It does so in two phases:

\begin{itemize}
\item Forward phase: For one instance of training, the inputs are fed forward through the network using the current weights and the final output is compared to the training labels. The derivative of the loss function is then computed.
\item Backward phase: This phase learns how the gradient of the loss function changes when the weights are varied. Starting at the output node, the algorithm goes backwards through the network (hence the name). The weights that give the steepest descent to the loss function are saved for the next training instance.  
\end{itemize}
This process of updating the weights is repeated until the loss function reaches convergence or a global minimum. The training data is cycled through in epochs. An epoch is defined when the entire data set is fed through the network. It is impractical to feed the entire data set into the network at once, so the training is split up into smaller more manageable batches. Finally, the number of batches needed to compete one epoch is referred to as the iterations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Convolutional Neural Networks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acp{CNN} are designed to work with grid-like input structures that exhibit
strong local spatial dependencies. Although most work with \acp{CNN}
involve image-based data, they can be applied to other spatially adjacent data
types such as time-series and text items. \acp{CNN} are defined by the use of a
convolution operation, a mathematical operation that expresses the amount
overlap between functions. Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel qhich is typically smaller in size than the input. The convolution is applied by shifting the kernel over the input, drawing out spatially important features between the
two. The distance by which the grid is shifted is known as
the stride and increasing it reduces the dimensionality of the
output. The output of the convolutional layer is then passed to an activation function.

@@

\begin{equation}
    L = -y \log(p) + (1 - y) \log(1-p),
    \label{eqn:gloss}
\end{equation}
where p is the networks output and y is the true output. 
To update the generator, a new batch of fake samples is generated by drawing new points in the latent space and passing this to the discriminator. The generators loss is computed by minimizing the discriminators loss averaged over the batch but with switched labels

\begin{equation}
    L_{G} = n^{-1} \sum\limits_{i=1}^n \log(1-D(G(\mathbf{z}_{i}))),
\end{equation}
where D is the discriminator and G is the generator.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional GANs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% introduce CGANs and ACGANs
%
To gain more control over what a GAN is able to generate, a conditional variant
of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra
information into the generator and discriminator such as a class label or
attribute label, $c$. This simple addition has shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}. We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube. For example e.g. $c=[0,1,0,0,0]$ represents the ring-down signal class. The training data and labels are drawn from a joint distribution $p_{real}(x,c)$, whereas when generating fake data we sample from $p(c)$ and $p(z)$ independently. While the generator and disriinmator now have two inputs $D(\mathbf{z},\mathbf{c})$ and $G(\mathbf{z},\mathbf{c})$ the networks are still trained via Eq. \eqref{eqn:gloss} as the discriminator only needs to output the realness/fakeness. 
Fig. \ref{fig:gan_comparison} shows the differences in inputs and outputs of a GAN compared with a \ac{CGAN}. We will be using a conditional GAN for this study.

\begin{figure}[h!]
    \begin{subfigure}{.5\textwidth}
     \centering
        \input{figures/GAN_diagram_vertical}
        \caption{GAN}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
     \centering
        \input{figures/ACGAN_diagram_vertical}
        \caption{CGAN}
    \end{subfigure}
    \caption{Comparison of the original GAN method and the
Conditional-GAN method. For CGANs the training data requires a label denoting
its class that is also fed to the generator which then learns to generate
waveforms based on the input label.~\chris{Overall it's a bit basic and doesn't indicate either the
2 competing training steps or any aspect of the loss or specify that $x$ and
$z$ (and $c$) are drawn from distributions already defined in the text. Maybe it's OK without
that. As for the CGAN, I'm troubled by the fact that there is only one $c$ box.
It implies that the same $c$ value is given to each real and fake $x$ data when
in fact each $x$ sample has it's own randomly drawn $c$ value.}} \label{fig:gan_comparison}
\end{figure}

~\chris{After describing the latent space meaning in the GAN section you need
to bring that together with a discussion of the entirely seperate class space
and how it is defined with reference to the on-hot encoded corners of a 5-D
vector space. Here is where you can inroduce the concept of the space and
mention the issue of probing the regions between the corners}

@@

% introduce the signal models
%
\ac{GW} burst signals remain an unmodelled phenomenon~\chris{as in the
introduction I think you need to make the distinction between unmodelled and
modelled burst analyses}, as such, current detection algorithms exploit the
fact that astrophysical signals will appear within data from multiple detectors
in coincidence and share the same waveform morphology.~\chris{I have added to
this first sentence but it still doesn't naturally lead intpo the next one} We
propose a signal generation scheme using a \ac{CGAN} trained on burst-like
waveforms. We call this \texttt{BurstGAN}~\chris{give reference to code repo
here} and is a \ac{CGAN} trained on five signal classes each spanning a range
of prior signal parameters. The signal classes are:

% list the 5 waveform classes
%
\begin{itemize}
%
\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
\tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
envelope characterised by a central frequency, $f_0$.~\chris{what about
amplitude, time of arrival and initial phase? For all the other classes too.}
%
\item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$
%
\item {\bf White-noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
variance Gaussian distribution and ahave a bounded frequency bandwidth $\Delta
f$ and duration $\tau$~\chris{no, they have a Gaussian envelope with a duration
parameter $tau$, we don't explicitly define the bandwidth}.
%
\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
duration parameter $\tau$.
%
\item {\bf Binary-black hole}: Simulated using the IMRPhenomD
waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
lie in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins and we fix
$m_1>m_2$. The mass distribution is approximated by a power law with
index of 1.6~\cite{Abbott_2019}. The signals are generated using random right
ascensions and declinations uniform over the sky and the inclinations are drawn
from the cosine of a uniform distribution in the range [-1,1].~\chris{OK, we
have an issue here. First the prior parameters and ranges are being defined
here rather than in the table with the other classes. Second, you are
randomising the sky in order to get random antenna patterns which only act to
change the relative amplitudes in multiple detectors - whcih we don't use any
more. So I would say that you shoudl only use the plus polarisation since it is
the same as the cross but pi/2 out of phase.}  
%
\end{itemize}
%
The location of the peak amplitude of the waveforms (corresponding to the
mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn to
be within [0.4, 0.6] sec from the start of the 1 sec time interval and all
training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
defined in~\cref{Tab:training_parms}.~\chris{Yes, those are the ranges but what
are the distributions?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Architecture details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Introduce some architecture features
%
Extensions to the original \ac{GAN} method such as the
\ac{DCGAN}~\cite{Radford2015} have been widely praised for enabling a stable
\ac{GAN} architecture. Most GANs now replace fully connected layers, where each
neuron is connect to all the neurons in the previous and next layer, with
convolutional layers. \acp{CNN}~\michael{capitalisation, not sure how it works
with the accronyms package}~\chris{I will fix this} are designed to work with
grid-like structures with close local dependencies like image and text based
data, however, there are examples of audio synthesis
work~\cite{DBLP:journals/corr/abs-1809-11096}.~\chris{this text sounds very
similar to the CNN text from earlier. Do you need this here? Can you simply say
that we are using a DCGAN architecture or say that our networks use
convolutional layers and then move on?}

% specifically define our architecture
%
We adopt the suggestions
of~\cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
one-dimensional convolution kernels on both the generator and
discriminator~\chris{what does this statment actually mean and why are you
opening the paragrpah with it?}.  The Generator model is fully convolutional,
upsampled using strided transposed~\chris{you mentioned strides before but not
transposing. Can you explain that aspect seomwhere earlier on.} convolutions
with batch normalisation~\chris{same here, can you mention it earlier} in the
first layer and ReLU~\chris{you can easily mention ReLU and other activations
earlier} activations throughout with the exception of the Tanh activation for
the output layer~\chris{why do you need this for the output? State that it is
to guarantee the output function is bound between [-1,1]}. Each transposed
convolutional layer uses a kernel size of $18\times 1$~\chris{by saying 18x1
you are saying that you are using a 2D kernel with width 1 but why not just say
you use a 1D kernel of size 18?} and stride of 2. The discriminator network
mirrors that of the generator without batch normalization~\chris{why?}, using
LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
downsampling~\chris{any reason for these choices?}. The discriminator output is
a single node with Sigmoid activation that can be interpreted as a probability
of the the signal being real. This model is trained with binary cross
entropy~\chris{how exactly if the output is 1 number rather than 2 (binary)?}.
The full architecture description can be seen in~\cref{Tab:hyperparameters}.
~\jordan{still too technical im not sure if we need to go into more detail on
each thing mentioned.} \michael{This para doesn't seem to technical to
me}~\chris{same here, not too technical but lacking detail and motivation for
choices.}
%~\chris{OK, very technically tight but too computer sciencey. Try to make it
%human readbale for a physicist and refer to the table of parameters in the
%appendix.}

% describe the hyperparameter tunings
%
Neural networks and subsequently \acp{GAN} have multiple parameters a developer
can tune when designing the model and these are referred to as hyperparameters.
The final network design used in this work comes from the use of trial and
error and the initial designs influenced by the available literature. We found
that the \ac{GAN} performed better with both networks having the same number of
layers and neurons which should~\chris{should? well does it?} encourage even
competition between the generator and discriminator.  After tuning the multiple
hyperparameters (see \cref{Tab:hyperparameters}), the \ac{GAN} was trained on
$10^5$ signals which contained an even mixture~\chris{be a bit more specific
about what an even mixture is - technically they are drawn from a categorical
distribution with equal propabilities for each class} of
sine-Gaussian~\chris{Gauss was a person so we have to capitalise his stuff},
ring-down, white noise bursts, Gaussian pulse and \acp{BBH} for 1000 epochs and
takes $\Or$(2) days to train~\chris{on what? be specific}. A larger batch size
saw a small increase in performance~\chris{what is performance in this case} at
the cost of training speed and we decided that 128~\chris{128 what? Also, why
pick on batch size as the thing to comment on here? What about learning rate,
kernel size, etc...} was a fair compromise.

\begin{comment}
include Plot_NN to show generator architecture
\end{comment}

~\chris{Please add a loss plot and use a paragrpah to describe what is going
on.}

>>>>

% basic network structure
%
A neural network contains many single neurons connected in a layered structure
as shown in~\cref{fig:network}. The activation's of the first layer (or
input layer) act as the inputs to the second layer and so on until the output
layer. Multi-layered neural networks have intermediate layers between the input
and output stages dubbed the hidden layers.
% the cost or loss function
%
The output of a single neuron is gives a
prediction that can be compared to the real value through a loss (also known as a
cost) function. The network must work to minimise this function by updating the weights in the negative
direction of the loss gradient in a process referred to as gradient
descent \cite{ruder2016overview}. The training process for a single layered network is easy to compute as the weights relate directly to the gradient of the loss function the network is trying to minimise. For deeper architectures, the loss is a complicated function of all the weights in all the layers. The backpropagation \cite{Nielsen1992} algorithm acts over the many paths from node to output. It does so in two phases:

\begin{itemize}
\item Forward phase: For one instance of training, the inputs are fed forward through the network using the current weights and the final output is compared to the training labels. The derivative of the loss function is then computed.
\item Backward phase: This phase learns how the gradient of the loss function changes when the weights are varied. Starting at the output node, the algorithm goes backwards through the network (hence the name). The weights that give the steepest descent to the loss function are saved for the next training instance.  
\end{itemize}
This process of updating the weights is repeated until the loss function reaches convergence or a global minimum. The training data is cycled through in epochs. An epoch is defined when the entire data set is fed through the network. As it is impractical to feed the entire data set into the network at once, so the training is split up into smaller more manageable batches. Finally, the number of batches needed to compete one epoch is referred to as the iterations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Convolutional Neural Networks}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acp{CNN} are designed to work with grid-like input structures that exhibit
strong local spatial dependencies. Although most work with \acp{CNN}
involve image-based data, they can be applied to other spatially adjacent data
types such as time-series and text items. \acp{CNN} are defined by the use of a
convolution operation, a mathematical operation that expresses the amount
overlap between functions. Much like traditional neural networks the convolution operation in this context involves multiplying the input by an array of weights, called a filter or a kernel qhich is typically smaller in size than the input. The convolution is applied by shifting the kernel over the input, drawing out spatially important features between the
two. The distance by which the grid is shifted is known as
the stride and increasing it reduces the dimensionality of the
output, this process is know as down sampling. Alternatively, up sampling the inputs can be achieved using a transposed convolution \cite{dumoulin2016guide}.   The output of the convolutional layer is then passed to an activation function. For deep neural networks, techniques like BatchNormalisation \cite{ioffe2015batch} which standardise the inputs to a layer and SpatialDropout \cite{tompson2014efficient} which sever connections between neurons can both help to stabilise learning.

@@

\begin{equation}
    L = -y \log(\hat{y}) + (1 - y) \log(1-\hat{y}),
    \label{eqn:crossentropy}
\end{equation}
where $\hat{y}$ is the network prediction and $y$ is the true output. While training the discriminator, D, on real data, we set $y = 1$ and $\hat{y} = D(x)$ which from eqn. \ref{eqn:crossentropy} gives $L(D(x),1) = \log(D(x))$. While training on fake data produced by the generator, G, $y = 0$ and $\hat{y} = D(G(z))$ and so, $L(D(G(z)),0) = \log(1-(D(G(z))))$. \jordan{whole derivation unnecessary?} Since the objective of the discriminator is to correctly classify fake and real data these equations should be maximised, while the goal of the generator should be to minimize these equations. This gives the \ac{GAN} loss as

\begin{equation}
   \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{\text{data}}}(\mathbf{x})} [\text{log} D(\mathbf{x})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))],
 \label{equation:GANloss}
 \end{equation}
where $p_{\text{\text{data}}}(\mathbf{x})$ is the distribution of real data and $p_{\text{z}}(\mathbf{z})$ is the distribution of the latent space.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional GANs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% introduce CGANs and ACGANs
%
To gain more control over what a GAN is able to generate, a conditional variant
of \acp{GAN} named \acp{CGAN}~\cite{cgan} was introduced by feeding in extra
information into the generator and discriminator such as a class label or
attribute label, $c$. This simple addition has shown to work well in practice, for instance in image-to-image translation~\cite{isola2016imagetoimage}. We defined the classes in one-hot encoding framework, that is, each class resides at the corner points of a 5 dimensional cube. For example e.g. $c=[0,1,0,0,0]$ represents the ring-down signal class. The training data and labels are drawn from a joint distribution $p_{data}(\mathbf{x},\mathbf{c})$, whereas when generating fake data we sample from $\mathbf{c}$ and $p_{z}(\mathbf{z})$ independently. \href{equation:GANloss} is modified to include the class labels 
~
\begin{equation}
   \mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{\text{data}}}(\mathbf{x})} [\text{log} D(\mathbf{x|c})] + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z|c})))].
 \label{equation:CGANloss}
 \end{equation}
Fig. \ref{fig:gan_comparison} shows the differences in inputs and outputs of a GAN compared with a \ac{CGAN}. We will be using a conditional GAN for this study.

\begin{figure}[h!]
    \begin{subfigure}{.5\textwidth}
     \centering
        \input{figures/GAN_diagram_vertical}
        \caption{GAN}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
     \centering
        \input{figures/ACGAN_diagram_vertical}
        \caption{CGAN}
    \end{subfigure}
    \caption{Comparison of the original GAN method and the
Conditional-GAN method. For CGANs the training data requires a label denoting
its class that is also fed to the generator which then learns to generate
waveforms based on the input label.}
\begin{comment}
~\chris{Overall it's a bit basic and doesn't indicate either the
2 competing training steps or any aspect of the loss or specify that $x$ and
$z$ (and $c$) are drawn from distributions already defined in the text. Maybe it's OK without
that. As for the CGAN, I'm troubled by the fact that there is only one $c$ box.
It implies that the same $c$ value is given to each real and fake $x$ data when
in fact each $x$ sample has it's own randomly drawn $c$ value.}
\end{comment}
\label{fig:gan_comparison}
\end{figure}

@@

% introduce the signal models
%
We propose a signal generation scheme using a \ac{CGAN} trained on burst-like
waveforms. We call this \texttt{BurstGAN} \cite{jordan_git} and is a \ac{CGAN} trained on five signal classes each spanning a range
of prior signal parameters. The signal classes are:

% list the 5 waveform classes
%
\begin{itemize}
%
\item {\bf Sine-Gaussian}: $h_{\text{sg}}(t) = A \exp\left[ - (t-t_{0})^2 /
\tau^2 \right] \sin (2 \pi f_0 (t-t_0))$, a sinusoidal wave with a Gaussian
envelope characterised by a central frequency, $f_0$, amplitude, $A$, time of arrival, $t_{0}$. 
%
\item {\bf Ring-down}: $h_{\text{rd}}(t) = A \exp \left[-{(t-t_0)} / {\tau}
\right] \sin(2 \pi f_0 (t-t_0))$, with frequency $f_0$ and duration $\tau$, amplitude, $A$, time of arrival, $t_{0}$. 
%
\item {\bf White-noise bursts}: $h_{\text{wn}}(t_j) = Ag_j\exp\left[ -
(t-t_{0})^2 / \tau^2 \right]$ where $g_j$ are drawn from a zero mean unit
variance Gaussian distribution with a Gaussian envelope of duration $tau$.
%
\item {\bf Gaussian pulse}: $h_{\text{gp}}(t) = \exp(-t^2 / \tau^2)$ with
duration parameter $\tau$.
%
\item {\bf Binary-black hole}: Simulated using the IMRPhenomD
waveform~\cite{Khan_2016} routine from LALSuite~\cite{lalsuite} which models
the inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses
lie in the range of [5,70] $\textrm{M}_{\odot}$ with zero spins and we fix
$m_1>m_2$. The mass distribution is approximated by a power law with
index of 1.6~\cite{Abbott_2019}. The inclinations are drawn
such that the cosine of the angles lies uniformly in the range [-1,1] and we only use the plus polarisation.
%
\end{itemize}
%
The location of the peak amplitude of the waveforms (corresponding to the
mid-points of all but the ring-down and \ac{BBH} classes) are randomly drawn from a uniform distribution to
be within [0.4, 0.6] sec from the start of the 1 sec time interval and all
training waveforms are sampled at 1024 Hz.  The parameter prior ranges are
defined in~\cref{Tab:training_parms}. All training data is rescaled such that their amplitudes peak at 1.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Architecture details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Introduce some architecture features
%
For this work we use a \ac{DCGAN}~\cite{Radford2015} architecture. The generator model is fully convolutional,
upsampled using strided transposed convolutions
with batch normalisation in the
first layer and ReLU activations throughout with the exception of the Tanh activation for
the output layer. The use of Tanh guarantees the output function is bound between [-1,1]. Each transposed
convolutional layer uses a kernel size of 18 and stride of 2. The discriminator network
mirrors that of the generator without batch normalization, using
LeakyReLU activations, SpatialDropout, and a 2-stride convolution for
downsampling. The discriminator output is a single node with Sigmoid activation that can be interpreted as a probability of the the signal being real and both models are trained with binary cross
entropy. The full architecture description can be seen in~\cref{Tab:hyperparameters}.

% describe the hyperparameter tunings
%
Neural networks and subsequently \acp{GAN} have multiple parameters a developer
can tune when designing the model and these are referred to as hyperparameters.
The final network design used in this work comes from the use of trial and
error and the initial designs influenced by the available literature. We found
that the \ac{GAN} performed better with both networks having the same number of
layers and neurons which encourages even
competition between the generator and discriminator.  After tuning the multiple
hyperparameters (see \cref{Tab:hyperparameters}), the \ac{GAN} was trained on
$10^5$ signals  drawn from a categorical
distribution with equal propabilities for each class of
sine-Gaussian,
ring-down, white noise bursts, Gaussian pulse and \acp{BBH}. \jordan{add how many epochs trained for, on what hardware and how long}

As \acp{GAN} are trained by updating one model at the expense of the other, they can be hard to train. The goal of GAN training is to find an equilibrium between the two models, if this cannot be found then it is said that the \ac{GAN} has failed to converge. One way to diagnose \acp{GAN} during the development process is to keep track of the loss over time. Loss plots, for example, as seen in fig. \ref{fig:lossplot} can help to identify common failure modes or to check if the \ac{GAN} has indeed converged. There is currently no notion of early stopping in \acp{GAN}, instead, training is halted after convergence and by visually inspecting the generations.

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Paper_draft/figures/Screenshot 2020-09-11 at 16.52.47.png}
    \caption{Line plots of the discriminator (blue) and generator (orange) loss v iterations. Early in training the losses oscillates as both models attempt to find their equilibrium, after which, both losses vary around 0.7.}
    \label{fig:lossplot}
\end{figure}
